\documentclass[12pt]{article}
\usepackage{fullpage}

\setlength{\parskip}{0.3cm}
\setlength{\parindent}{0cm}

\begin{document}

\section*{Project Overview}

This document outlines our project's approach to optimizing cohere embedding through graph comparison and its application in essay reasoning. The project aims to enhance the understanding of logical relations between events and people, going beyond the semantic similarity comparison typically offered by embedding APIs.

\begin{enumerate}
    \item \textbf{Graph For Education:}The graph in our project helps visitors easily understand the logical connections in a story. It shows how events and characters are related, making complex stories simple and clear. This makes it easier for visitors to follow the plot and see how different parts of the story fit together.
    \item \textbf{Graph Comparison Optimization:} The project introduces an innovative approach to cohere embedding by utilizing graph-based comparisons and matrix operations. Unlike conventional methods that focus solely on semantic similarities, our approach delves into the logical connections between various elements within texts. This involves analyzing the interactions and relationships between events and individuals, providing a more nuanced understanding of the underlying narrative structure.
    
    \item \textbf{Application in Essay Reasoning:} Utilizing the knowledge from our graph comparison method, this project significantly aids essay reasoning. It generates historical narratives as examples for reasoning, improving essay argument quality and providing contextually relevant historical instances.
\end{enumerate}

\end{document}
